\MakeUppercase{Layered $H$-Partitions of $k$-Planar Graphs} \thanks{This work was partly funded by NSERC and MRI.}

### 2019-05-06 k-planar.tex
Cleaning up

Next we describe a tree decomposition $(B_x:x\in V(K))$ of $H$.  (Don't be put off here by the fact that $V(H)=V(K)$, this is actually helpful because the subtree $K[x]$ will be rooted at $x$).  We claim that, for every edge $xz\in V(H)$, $x$ is an ancestor of $z$ (or vice-versa).  Indeed, this follows from the same argument used to show that $S_x$ is a partition.  If neither $x$ nor $z$ is an ancestor of the other, then any edge $vw$ with $v\in S_x$ and $w\in S_z$ contains a vertex of $Y_a$ for some common ancestor $a$ of $x$ and $z$. But this implies that neither $v$ nor $w$ appears in $S_x$ nor $S_z$.

>>>>

Next we describe a tree decomposition $(B_x:x\in V(K))$ of $H$.  We deliberately use the same node set $V(H)=V(K)$ here, because the subtree $K[x]:=K[\{z:x\in B_z\}]$ will be rooted at $x$.  We claim that, for every edge $xy\in V(H)$, $x$ is an ancestor of $y$ (or vice-versa).  Suppose that this is not the case and that $xy\in E(H)$ but neither $x$ nor $y$ is an ancestor of the other.  Then, since $xy\in E(H)$, there must exist an edge $vw\in E(G)$ such that $v\in S_x$ and $w\in S_y$.

Since $v\in S_x$, $v\in V(N_x)$ and similarly $w\in V(N_y)$.  Since neither $x$ nor $y$ are ancestors of each other, the interiors of $F_x$ and $F_y$ are disjoint.  If $v$ is in the interior $V(N_x)\setminus V(F_x)$ of $F_x$ then the edge $vw$ crosses $F_x$ and by (PR\ref{ancestor-boundary}) $v$ appears at some ancestor $a$ of $x$. (The node $a$ is the lowest node for which $v,w\in V(N_a)$.)  But this contradicts the assumption that $v\in S_x$, so it must be that $v\in V(F_x)$. This is also a contradiction, since (PR\ref{ancestor-boundary}) then implies that $v\in Y_a$ and therefore appears at $a$ for some $K$-ancestor $a$ of $x$, which contradicts the assumption that $v\in V(N_x)$.
